Title

### 2015-12-10 paper/paper.tex
done moving things around, still need to expand on my sections in 6
and move greedy search content earlier in the paper
listof{tables,figures} is magically working now. i did nothing. go tex

\begin{document}
\maketitle
\tableofcontents
\listofalgorithms
\pagebreak

@@

\subsection{Subgraph Ordering}

@@

@@

@@

\section{Evaluation of Scoring Modules}
\subsection{Subgraph Selection}
\subsection{Subgraph Ordering}

\section{Experiments}

>>>>

\begin{document}
\maketitle
\tableofcontents
\listoffigures
\listofalgorithms
\listoftables
\pagebreak

@@

\subsection{Subgraph Ordering}
\subsubsection{Problem Description}

@@

\subsubsection{Training}

@@

\subsubsection{Testing}

For subgraph ordering, we use Kendall's tau metric as our evaluation function.
For each test example, we compute the Kendall tau distance between a random
ordering and the correct ordering, to use as a baseline. Then, we perform a
greedy search discrete optimization as described above using the subgraph
ordering model to compute the scores of the various orderings.

The mean, standard deviation, min and max for both the baseline and greedy
approach are reported in the table below.

\begin{table}
\centering
\begin{tabular}{|r|c|c|c|c|c|}
\hline
Approach & Mean  & Std.  & Min & Max \\ \hline\hline
Baseline & 5.009 & 2.091 & 0   & 10  \\ \hline
Greedy   & 1.360 & 0.910 & 0   & 5   \\ \hline
\end{tabular}
\caption{Evaluation results for Subgraph Ordering}
\end{table}

@@

\subsection{Pipeline}

To evaluate the pipeline as a whole, we used a revised Kendall's tau metric, in
accordance with \cite{lapata2006automatic}.
